\clearpage
\begin{thebibliography}{99}

\bibitem{martello2000}
Martello S., Pisinger D., Vigo D. The Three-Dimensional Bin Packing Problem // Operations Research. 2000. Vol. 48, No. 2. P. 256--267. DOI: \url{https://doi.org/10.1287/opre.48.2.256.12386}.

\bibitem{faroe2003}
Faroe O., Pisinger D., Zachariasen M. Guided Local Search for the Three-Dimensional Bin-Packing Problem // INFORMS Journal on Computing. 2003. Vol. 15, No. 3. P. 267--283.

\bibitem{pisinger2010}
Pisinger D., Ropke S. Large Neighborhood Search // Handbook of Metaheuristics. 2nd ed. Springer, 2010. P. 399--420.

\bibitem{wassenhove1982}
Dyckhoff H., Finke U. Cutting and Packing in Production and Distribution: Typology and Bibliography. Heidelberg: Physica-Verlag, 1992. 248 p.

\bibitem{coffman1997}
Coffman E. G., Garey M. R., Johnson D. S. Approximation Algorithms for Bin Packing: A Survey // Approximation Algorithms for NP-Hard Problems. Boston: PWS Publishing, 1997. P. 46--93.

\bibitem{lodi2002}
Lodi A., Martello S., Vigo D. Recent Advances on Two-Dimensional Bin Packing Problems // Discrete Applied Mathematics. 2002. Vol. 123. P. 379--396.

\bibitem{crainic2008}
Crainic T. G., Perboli G., Tadei R. Extreme Point-Based Heuristics for Three-Dimensional Bin Packing // INFORMS Journal on Computing. 2008. Vol. 20, No. 3. P. 368--384.

\bibitem{gendreau2006}
Gendreau M., Iori M., Laporte G., Martello S. A Tabu Search Algorithm for a Routing and Container Loading Problem // Transportation Science. 2006. Vol. 40, No. 3. P. 342--350.

\bibitem{zhang2024}
Zhang Y., Wang X., Liu Z. A Novel Approach for Solving 3D Bin Packing Problem by Integrating a Generative Adversarial Network with a Genetic Algorithm // Scientific Reports. 2024. DOI: \url{https://doi.org/10.1038/s41598-024-56699-7}.

\bibitem{kaggle_sleigh}
Packing Santa's Sleigh // Kaggle: соревнование по задаче трехмерной упаковки [Электронный ресурс]. URL: \url{https://www.kaggle.com/competitions/packing-santas-sleigh/overview} (дата обращения: 27.04.2026).

\bibitem{project_repo}
DrogoZZZZ. 3D Bin Packing [Электронный ресурс]: GitHub-репозиторий проекта. URL: \url{https://github.com/DrogoZZZZ/3D_bin_packing} (дата обращения: 26.05.2026).

\end{thebibliography}
